CA Affordabulity

### 2020-09-20 paper.Rmd
update

own <- ear %>% 
    filter(QuestionName == "Population" | 
                QuestionName == "Water System Classification" |
                QuestionName == "Water System Ownership" |
                QuestionName == "IsWholesaler") %>% 
    mutate(QuestionID=paste0("q",QuestionID)) %>%
    select(PWSID, Year, QuestionName,  QuestionResults) %>% 
    distinct(PWSID, Year, QuestionName, .keep_all=TRUE) %>%
    pivot_wider(names_from = QuestionName,
                values_from = QuestionResults) %>%
    group_by(PWSID) %>%
    mutate(maxYear=max(Year)) %>%
    ungroup() %>%
    filter(Year == maxYear) %>%
    filter(is.na(IsWholesaler)) %>%
 #   mutate(Population = as.numeric(Population)) %>%
    filter(`Water System Classification`=="Community Water System")

own_inv <- left_join(inv,own,by="PWSID")

>>>>

questions <- c("Population",
               "Water System Classification",
               "Water System Ownership",
               "IsWholesaler",
               "WR Type",
               "WR 6 HCF DW Charges",
               "WR 12 HCF DW Charges",
               "T Potable Total",
               "WR SHUT_OFFS Once No Collect",
               "WR SHUT_OFFS Once SF Total",
               "WR SHUT_OFFS More Than Once MF Total",
               "WR SHUT_OFFS More Than Once SF Total",
               "WR SHUT_OFFS Once MF Total",
               "WR LL Subsidies",
               "WR LL Eligibility-Low Income",
               "WR LL Eligibility-Disabled",
               "WR LL Eligibility-Medical",
               "WR LL Eligibility-Other",
               "WR LL Eligibility-Senior",
               "WR LL Benefit Form",
               "WR LL Funded",
               "DIST Probs SC BL Num",
                "DIST Probs SC BL Investigated",
                "DIST Probs SC BL Reported to District",
                "DIST Probs SC BL Cause",
                "DIST Probs Main BL Num",
                "DIST Probs Main BL Investigated",
                "DIST Probs Main BL Reported to District",
                "DIST Probs Main BL Cause",
                "DIST Probs WO Num",
                "DIST Probs WO Investigated",
                "DIST Probs WO Reported to District",
                "DIST Probs WO Cause",
                "DIST Probs BWO Num",
                "DIST Probs BWO Investigated",
                "DIST Probs BWO Reported to District",
                "DIST Probs BWO Cause",
                "DIST Probs Total Num",
                "DIST Probs Total Investigated",
                "DIST Probs Total Reported to District",
                "DIST Probs Comments",
                "TREATMENT GW Problems",
                "TREATMENT SW Problems",
                "SLI Lead Number",
                "SLI Lead Total Length",
                "SLI Fittings NOT lead pipe",
                "SLI Fittings Lead pipe",
                "SLI Total Lead Service Lines",
                "SLI Cast Number",
                "SLI Copper Number",
                "SLI Ductile Number",
                "SLI Fittings Unknown",
                "SLI Galvanized Number",
                "SLI HDPE Number",
                "SLI Identify material 1",
                "SLI Identify material 2",
                "SLI Identify material 3",
                "SLI Identify material 4",
                "SLI Material 1 Number",
                "SLI Material 2 Number",
                "SLI Material 3 Number",
                "SLI Material 4 Number",
                "SLI Polybutylene Number",
                "SLI Polyethylene Number",
                "SLI Polyvinyl Number",
                "SLI TA cement Number",
                "SLI Total Lead Service Lines",
                "SLI Total Service Connections",
                "SLI Total Service Lines",
                "SLI Unknown Number",
                "SLI Unknown Total Length",
                "DIST Infra Rehabilitation Comments",
                "DIST Infra Rehabilitation Expenditure",
                "DIST Infra Rehabilitation Not Tracked",
                "DIST Infra Rehabilitation Num Leaks",
                "DIST Infra Rehabilitation Portion",
                "DIST Infra Rehabilitation Real Loss",
                "DIST Infra renewal table unit",
                "DIST Infra Repair Comments",
                "DIST Infra Repair Expenditure",
                "DIST Infra Repair Not Tracked",
                "DIST Infra Repair Num Leaks",
                "DIST Infra Repair Portion",
                "DIST Infra Repair Real Loss",
                "DIST Infra Replacement Comments",
                "DIST Infra Replacement Expenditure",
                "DIST Infra Replacement Not Tracked",
                "DIST Infra Replacement Num Leaks",
                "DIST Infra Replacement Portion",
                "DIST Infra Replacement Real Loss",
                "DIST Infra Total Comments",
                "DIST Infra Total Expenditure",
                "DIST Infra Total Not Tracked",
                "DIST Infra Total Num Leaks",
                "DIST Infra Total Portion",
                "DIST Infra Total Real Loss",
                "Cur Total Connections",
                "Inactive Connections",
                "Connections meter records kept",
                "Connections SF with outdoor irrigation meters",
                "Connections MF with outdoor irrigation meters",
                "Connections customers with indoor submeters",
                "Connections Comment",
                "DIST Interv Booster Average",
                "DIST Interv Booster Comments",
                "DIST Interv Booster Expenditure",
                "DIST Interv Booster Not Tracked",
                "DIST Interv Booster Portion",
                "DIST Interv Other Average",
                "DIST Interv Other Comments",
                "DIST Interv Other Expenditure",
                "DIST Interv Other Not Tracked",
                "DIST Interv Other Portion",
                "DIST Interv Pressure R Average",
                "DIST Interv Pressure R Comments",
                "DIST Interv Pressure R Expenditure",
                "DIST Interv Pressure R Not Tracked",
                "DIST Interv Pressure R Portion",
                "DIST Interv Pressure T Average",
                "DIST Interv Pressure T Comments",
                "DIST Interv Pressure T Expenditure",
                "DIST Interv Pressure T Not Tracked",
                "DIST Interv Pressure T Portion",
                "DIST Interv Reduced Average",
                "DIST Interv Reduced Comments",
                "DIST Interv Reduced Expenditure",
                "DIST Interv Reduced Not Tracked",
                "DIST Interv Reduced Portion",
                "DIST Interv Total Average",
                "DIST Interv Total Comments",
                "DIST Interv Total Expenditure",
                "DIST Interv Total Not Tracked",
                "DIST Interv Total Portion",
                "DIST 5 Year Expenditure",
                "DIST 5 Year Summary Comments",
                "DIST 5 Year Total Leaks",
                "DIST 5 Year Water Loss" 
               )

own <- ear %>% 
    filter(QuestionName %in% questions) %>% 
    group_by(PWSID,Year,QuestionName) %>%
     mutate(maxYear=max(Year)) %>%
    ungroup() %>%
  #  filter(Year == maxYear) %>%
   select(PWSID, Year, QuestionName,  QuestionResults) %>% 
    distinct(PWSID, Year, QuestionName, .keep_all=TRUE) %>%
    pivot_wider(names_from = QuestionName,
                values_from = QuestionResults) %>%

    filter(is.na(IsWholesaler)) %>%
 #   mutate(Population = as.numeric(Population)) %>%
    filter(`Water System Classification`=="Community Water System")
